---
title: "Single versus mixed inoculations of bacteria on Lemna minor"
author: "Jason Laurich and Megan Frederickson"
date:  Sys.Date()
output: github_document
editor_options: 
  chunk_output_type: console
---

SECTION 1: Upload packages

```{r Packages, message=FALSE, warning=FALSE}
library(lme4) # mixed effects models
library(lmerTest) # get results of lmer models
library(tidyverse) #manipulating data frames
library(cowplot) # luxury plotting
library(emmeans) # allows extraction of bacteria-specific regression estimates
library(ggrepel) # fine tune figures
library(ggtext) # fine tune figures
library(knitr) # render markdown
library(kableExtra) # exports tables to LaTeX format
```

SECTION 2: Upload data for 2020 and 2019 experiments.

```{r Data, message=FALSE, warning=FALSE}
#####################Load 2020 data#######################
df.CW<-read.table('CW_mixed_inoculation_data.txt', header=F, na.strings="", sep="\t")
names(df.CW)<-c('pop','plt','bac','id','frd0','pix0','per0','grn0','grnper0','frd1','pix1','per1','grn1','grnper1','abs')

#Fix the structure for bacterial inoculation and plant
df.CW$bac <- factor(df.CW$bac, levels = c("Control", "1", "2", "3", "4", "5","6","7","8","9","10","All10"))
df.CW$plt <- as.factor(df.CW$plt)

# Add in edge effects. So for each 24 well plate, all but 6,7,10,11,14,15,18, and 19 are edge.
edge<-c(rep("Y",5), rep("N",2), rep("Y",2),rep("N",2), rep("Y",2), rep("N",2), rep("Y",2),rep("N",2), rep("Y",5))

#Final plate has 8 samples only
edge2<-rep(edge,38)
edge2<-c(edge2, rep("Y",5), rep("N",2), "Y")
df.CW$edge<-edge2

df.CW$edge <- as.factor(df.CW$edge)

plate<-vector()
# Create vector for plate - 38 full, 39th with 8 wells
for (i in 1:38){
  plate<-c(plate, rep(i,24))
}
plate<-c(plate,rep(39,8))

df.CW$plate <- plate
df.CW$plate <- as.factor(df.CW$plate)

#Take out errors (pipetting errors, wrong bacteria)
df.CW<-df.CW[-c(453,494,798),]

# Calculate growth.
df.CW$Grt<-df.CW$pix1 - df.CW$pix0

# Log abs count
df.CW$logabs<-log(df.CW$abs)

#Let's create separate dataframes for each population # Going to get the label 2020
df.C.2020<-subset(df.CW, df.CW$pop== "Churchill")
df.W.2020<-subset(df.CW, df.CW$pop== "Wellspring")

# Change factor order of bacteria to reflect their effects on duckweed growth.
#First, let's change the order of bacteria, ranked by effect. 
df.C.2020$bac<- factor(df.C.2020$bac, levels = c("Control","1","8","6","3","7","10","9","4","5","2","All10"))
# Assign names from sequencing
levels(df.C.2020$bac) <- c("Control", "Flavobacterium \nsuccinicans 1","Bosea \nmassiliensis","Aeromonas \nsalmonicida","Ohtaekwangia \nkoreensis","Flavobacterium \nsuccinicans 2","Falsiroseomonas \nstagni","Parasediminibacterium \npaludis","Arcicella sp.","Microbacterium \noxydans","Pseudomonas \nprotogens","All 10 bacteria")

df.W.2020$bac<- factor(df.W.2020$bac, levels = c("Control","2","8","1","9","6","3","5","4","7","10","All10"))
levels(df.W.2020$bac) <- c("Control","Sphingomonas \npituitosa 1","Flaviflagellibacter \ndeserti","Rhizobium \nrosettiformans","Rhizorhabdus \nwittichii 1","Rhizobium \ncapsici 1","Pseudomonas \nprotogens","Rhizorhabdus \nwittichii 2","Rhizobium \ncapsici 2","Sphingomonas \npituitosa 2","Fervidobacterium \nriparium","All 10 bacteria")

df2020 <- rbind(df.C.2020, df.W.2020)

#####################Load 2019 data#######################

df.CKW<-read.table('July2019CKW.txt', header=F, na.strings="", sep="\t")
names(df.CKW)<-c('pop','bac','id','frd0','pix0','per0','grn0','grnper0','frd1','pix1','per1','grn1','grnper1','notes','algae_lvl')

#Fix the structure
df.CKW$pop<-as.factor(df.CKW$pop)
df.CKW$bac<-as.factor(df.CKW$bac)

# Add in edge (15 plates)
edge3<-rep(edge,15)
df.CKW$edge<-edge3

df.CKW$edge <- as.factor(df.CKW$edge)
df.CKW$algae_lvl<-as.factor(df.CKW$algae_lvl)

plate2<-vector()
# Create vector for plate
for (i in 1:15){
  plate2<-c(plate2, rep(i,24))
}

df.CKW$plate <- plate2
df.CKW$plate <- as.factor(df.CKW$plate)

df.CKW$Grt<-df.CKW$pix1 - df.CKW$pix0

# We want to include algal level as an ordinal variable.
df.CKW$alg.ord<- factor(df.CKW$algae_lvl, order = TRUE, levels = c("None","Low", "Med", "High"))

# Let's break this down by population.
df.C.2019<-subset(df.CKW, df.CKW$pop== "Churchill")
df.K.2019<-subset(df.CKW, df.CKW$pop== "Kelso")
df.W.2019<-subset(df.CKW, df.CKW$pop== "Wellspring ")

# Change factor order of bacteria to reflect their effects on duckweed growth.
#First, let's change the order of bacteria, ranked by effect. 
df.C.2019$bac<- factor(df.C.2019$bac, levels = c("0","7","8","5","6","10","4","9","2","1","3","All"))
# Assign names from sequencing
levels(df.C.2019$bac) <- c("Control","Aeromonas \nsalmonicida 1","Aeromonas \nsalmonicida 2","Microbacterium sp.","Parasediminibacterium \npaludis","Flavibacterium \nsuccinicans 1","Arcicella sp.","Falsiroseomonas \nstagni","Pseudomonas \nprotogens","Flavibacterium \nsuccinicans 2","Ohtaekwangia \nkoreensis","All 10 bacteria")

df.K.2019$bac<- factor(df.K.2019$bac, levels = c("0","8","6","7","3","9","2","5","1","4","10","All"))
levels(df.K.2019$bac) <- c("Control","Pseudomonas \nprotogens","Flavobacterium \nbranchiicola","Pseudomonas \nbaetica","Rhizobium sp.","Pseudacidovorax \nintermedius","Rhizobium \nrosettiformans","Flavobacterium \npanici 1","Flavobacterium \npanici 2","Flavobacterium \npanici 3","Pseudomonas \nsesami","All 10 bacteria")

df.W.2019$bac<- factor(df.W.2019$bac, levels = c("0","8","5","3","2","4","6","9","7","1","10","All"))
levels(df.W.2019$bac) <- c("Control","Rhizobium sp.","Agrobacterium sp.","Rhizobium \nrosettiformans 1","Rhizobium \nrhizophilum","Rhizobium \nrosettiformans 2","Rhizobium \nhelianthi","Sphingomonas \npituitosa","Rhizorhabdus \nwittichii","Rhizobium \nglycinendophyticum","Phenylobacterium \npanacis","All 10 bacteria")

df2019 <- rbind(df.C.2019, df.K.2019, df.W.2019)
```

SECTION 3: Plant growth models and figures

First, let's model the data. 

```{r Duckweed growth models}

#Churchill 2019
lmer.grt.C2019<-lmer(pix1 ~ pix0 + bac + alg.ord + (1|edge) + (1|plate), data=df.C.2019)
anova(lmer.grt.C2019, type=3)
ranova(lmer.grt.C2019)
summary(lmer.grt.C2019)
plot(lmer.grt.C2019)

#Try running an ANCOVA style model (e.g. checking for variation in slope effects of pix0vpix1 for each bac.)
lmer.grt.C2019.2<-lmer(pix1 ~ pix0*bac + alg.ord + (1|edge) + (1|plate), data=df.C.2019)
anova(lmer.grt.C2019.2)
ranova(lmer.grt.C2019.2)
summary(lmer.grt.C2019.2)
plot(lmer.grt.C2019.2)

#Kelso 2019
lmer.grt.K2019<-lmer(pix1 ~ pix0 + bac + alg.ord + (1|edge) + (1|plate), data=df.K.2019)
anova(lmer.grt.K2019)
ranova(lmer.grt.K2019)
summary(lmer.grt.K2019)
plot(lmer.grt.K2019)

lmer.grt.K2019.2<-lmer(pix1 ~ pix0*bac + alg.ord + (1|edge) + (1|plate), data=df.K.2019)
anova(lmer.grt.K2019.2)
ranova(lmer.grt.K2019.2)
summary(lmer.grt.K2019.2)
plot(lmer.grt.K2019.2)

#Wellspring 2019
lmer.grt.W2019<-lmer(pix1 ~ pix0 + bac + alg.ord + (1|edge) + (1|plate), data=df.W.2019)
anova(lmer.grt.W2019)
ranova(lmer.grt.W2019)
summary(lmer.grt.W2019)
plot(lmer.grt.W2019)

lmer.grt.W2019.2<-lmer(pix1 ~ pix0*bac + alg.ord + (1|edge) + (1|plate), data=df.W.2019)
anova(lmer.grt.W2019.2)
ranova(lmer.grt.W2019.2)
summary(lmer.grt.W2019.2)
plot(lmer.grt.W2019.2)

#Churchill 2020
lmer.grt.C2020<-lmer(pix1 ~ pix0 + bac + (1|edge) + (1|plate), data=df.C.2020)
anova(lmer.grt.C2020)
ranova(lmer.grt.C2020)
summary(lmer.grt.C2020)
plot(lmer.grt.C2020)

lmer.grt.C2020.2<-lmer(pix1 ~ pix0*bac + (1|edge) + (1|plate), data=df.C.2020)
anova(lmer.grt.C2020.2)
ranova(lmer.grt.C2020.2)
summary(lmer.grt.C2020.2)
plot(lmer.grt.C2020.2)

#Fronds added
df.C.2020$frdchg <- df.C.2020$frd1-df.C.2020$frd0
lmer.frd.C2020 <- lmer(frdchg~bac+ (1|edge)+(1|plate), data=df.C.2020)
summary(lmer.frd.C2020)

#Wellspring 2020
lmer.grt.W2020<-lmer(pix1 ~ pix0 + bac + (1|edge) + (1|plate), data=df.W.2020)
anova(lmer.grt.W2020)
ranova(lmer.grt.W2020)
summary(lmer.grt.W2020)
plot(lmer.grt.W2020)

lmer.grt.W2020.2<-lmer(pix1 ~ pix0*bac + (1|edge) + (1|plate), data=df.W.2020)
anova(lmer.grt.W2020.2)
ranova(lmer.grt.W2020.2)
summary(lmer.grt.W2020.2)
plot(lmer.grt.W2020.2)

#Fronds added
df.W.2020$frdchg <- df.W.2020$frd1-df.W.2020$frd0
lmer.frd.W2020 <- lmer(frdchg~bac+ (1|edge)+(1|plate), data=df.W.2020)
summary(lmer.frd.W2020)
```

Next, making a table of log response ratios of bacterial effects on plant growth. Reference for calculating LRR's: Hedges, L. V., Gurevitch, J., & Curtis, P. S. (1999). The meta-analysis of response ratios in experimental ecology. Ecology, 80(4), 1150-1156. Equation 1

```{r Log response ratios}
# 2020 data
# For each bacterial treatment, we need count, mean, and SD.
Sum_2020 <- subset(df2020, plt == "Y") %>% group_by(bac, pop) %>% dplyr::summarize(mean = mean(Grt, na.rm=T), sd = sd(Grt, na.rm=T), count=n(),  sem = sd/sqrt(count))

#Set the mean, count, and sd for the control group that everything else will be compared to
Sum_2020$control_mean <- as.numeric(ifelse(Sum_2020$pop == "Churchill", Sum_2020[Sum_2020$pop == "Churchill" & Sum_2020$bac == "Control", "mean"], Sum_2020[Sum_2020$pop == "Wellspring" & Sum_2020$bac == "Control", "mean"]))
   
Sum_2020$control_count <- as.numeric(ifelse(Sum_2020$pop == "Churchill", Sum_2020[Sum_2020$pop == "Churchill" & Sum_2020$bac == "Control", "count"], Sum_2020[Sum_2020$pop == "Wellspring" & Sum_2020$bac == "Control", "count"]))

Sum_2020$control_sd <- as.numeric(ifelse(Sum_2020$pop == "Churchill", Sum_2020[Sum_2020$pop == "Churchill" & Sum_2020$bac == "Control", "sd"], Sum_2020[Sum_2020$pop == "Wellspring" & Sum_2020$bac == "Control", "sd"]))
               
#Calculate LRRs and CIs
Sum_2020$LRR <- log(Sum_2020$mean)-log(Sum_2020$control_mean)
Sum_2020$LRRvar<-Sum_2020$sd^2/(Sum_2020$count*Sum_2020$mean^2) + Sum_2020$control_sd^2/(Sum_2020$control_count*Sum_2020$control_mean^2)
Sum_2020$LRRCIup <- Sum_2020$LRR+qnorm(0.975)*sqrt(Sum_2020$LRRvar)
Sum_2020$LRRCIdown <- Sum_2020$LRR-qnorm(0.975)*sqrt(Sum_2020$LRRvar)

#Make 2020 table
colnames(Sum_2020)[[1]] <- "Bacterial strain"
colnames(Sum_2020)[[12]] <- "Upper bound"
colnames(Sum_2020)[[13]] <- "Lower bound"
table_2020 <- kbl(Sum_2020[,c(2,1,10, 13,12)], format="latex", digits=4, caption="List of bacteria used in 2020 experiments, with log response ratios (LRR) and the lower and upper bounds of 95\\% confidence intervals for their effects on \\textit{Lemna minor} growth", booktabs=T, longtable=T, linesep = c('', '', '', '', '', '', '', '', '', '', '\\hline'))

# 2019 data
Sum_2019 <- df2019 %>% group_by(bac, pop) %>% dplyr::summarize(mean = mean(Grt, na.rm=T), sd = sd(Grt, na.rm=T), count=n(),  sem = sd/sqrt(count))
Sum_2019$pop <- trimws(Sum_2019$pop)

#Set the mean, count, and sd for the control group that everything else will be compared to
Sum_2019$control_mean <- as.numeric(ifelse(Sum_2019$pop == "Churchill", Sum_2019[Sum_2019$pop == "Churchill" & Sum_2019$bac == "Control", "mean"], ifelse(Sum_2019$pop == "Wellspring", Sum_2019[Sum_2019$pop == "Wellspring" & Sum_2019$bac == "Control", "mean"], Sum_2019[Sum_2019$pop == "Kelso" & Sum_2019$bac == "Control", "mean"])))
   
Sum_2019$control_count <- as.numeric(ifelse(Sum_2019$pop == "Churchill", Sum_2019[Sum_2019$pop == "Churchill" & Sum_2019$bac == "Control", "count"], ifelse(Sum_2019$pop == "Wellspring", Sum_2019[Sum_2019$pop == "Wellspring" & Sum_2019$bac == "Control", "count"], Sum_2019[Sum_2019$pop == "Kelso" & Sum_2019$bac == "Control", "count"])))

Sum_2019$control_sd <- as.numeric(ifelse(Sum_2019$pop == "Churchill", Sum_2019[Sum_2019$pop == "Churchill" & Sum_2019$bac == "Control", "sd"], ifelse(Sum_2019$pop == "Wellspring", Sum_2019[Sum_2019$pop == "Wellspring" & Sum_2019$bac == "Control", "sd"], Sum_2019[Sum_2019$pop == "Kelso" & Sum_2019$bac == "Control", "sd"])))
               
#Calculate LRRs and CIs
Sum_2019$LRR <- log(Sum_2019$mean)-log(Sum_2019$control_mean)
Sum_2019$LRRvar<-Sum_2019$sd^2/(Sum_2019$count*Sum_2019$mean^2) + Sum_2019$control_sd^2/(Sum_2019$control_count*Sum_2019$control_mean^2)
Sum_2019$LRRCIup <- Sum_2019$LRR+qnorm(0.975)*sqrt(Sum_2019$LRRvar)
Sum_2019$LRRCIdown <- Sum_2019$LRR-qnorm(0.975)*sqrt(Sum_2019$LRRvar)

#Make 2019 table
colnames(Sum_2019)[[1]] <- "Bacterial strain"
colnames(Sum_2019)[[12]] <- "Upper bound"
colnames(Sum_2019)[[13]] <- "Lower bound"
table_2019 <- kbl(Sum_2019[,c(2,1,10, 13,12)], format="latex", digits=4, caption="List of bacteria used in 2019 experiments, with log response ratios (LRR) and the lower and upper bounds of 95\\% confidence intervals for their effects on \\textit{Lemna minor} growth", booktabs=T, longtable=T, linesep = c('', '', '', '', '', '', '', '', '', '', '\\hline'))
```

```{r}
#Churchill 2019
Sum.C.2019 <- df.C.2019 %>% group_by(bac) %>% dplyr::summarize(mean = mean(Grt, na.rm=T), sd = sd(Grt, na.rm=T), count=n(),  sem = sd/sqrt(count))

lrr.C.2019<-Sum.C.2019[2:12,]
lrr.C.2019$LRR<-log(lrr.C.2019$mean) - log(Sum.C.2019$mean[1])
lrr.C.2019$var<-lrr.C.2019$sd^2/(lrr.C.2019$count*lrr.C.2019$mean^2) + Sum.C.2019$sd[1]^2/(Sum.C.2019$count[1]*Sum.C.2019$mean[1]^2)
lrr.C.2019$CI<-qnorm(0.975)*sqrt(lrr.C.2019$var)
lrr.C.2019$SE<-sqrt(lrr.C.2019$var)/sqrt(lrr.C.2019$count)
lrr.C.2019$CI_up <- lrr.C.2019$LRR+lrr.C.2019$CI
lrr.C.2019$CI_down <- lrr.C.2019$LRR-lrr.C.2019$CI
lrr.C.2019$Population <- "Churchill Marsh"

# Kelso 2019
Sum.K.2019 <- df.K.2019 %>% group_by(bac) %>% dplyr::summarize(mean = mean(Grt, na.rm=T), sd = sd(Grt, na.rm=T), count=n(),  sem = sd/sqrt(count))

lrr.K.2019<-Sum.K.2019[2:12,]
lrr.K.2019$LRR<-log(lrr.K.2019$mean) - log(Sum.K.2019$mean[1])
lrr.K.2019$var<-lrr.K.2019$sd^2/(lrr.K.2019$count*lrr.K.2019$mean^2) + Sum.K.2019$sd[1]^2/(Sum.K.2019$count[1]*Sum.K.2019$mean[1]^2)
lrr.K.2019$CI<-qnorm(0.975)*sqrt(lrr.K.2019$var)
lrr.K.2019$SE<-sqrt(lrr.K.2019$var)/sqrt(lrr.K.2019$count)
lrr.K.2019$CI_up <- lrr.K.2019$LRR+lrr.K.2019$CI
lrr.K.2019$CI_down <- lrr.K.2019$LRR-lrr.K.2019$CI
lrr.K.2019$Population <- "Kelso Pond"

# Wellspring 2019
Sum.W.2019 <- df.W.2019 %>% group_by(bac) %>% dplyr::summarize(mean = mean(Grt, na.rm=T), sd = sd(Grt, na.rm=T), count=n(),  sem = sd/sqrt(count))

lrr.W.2019<-Sum.W.2019[2:12,]
lrr.W.2019$LRR<-log(lrr.W.2019$mean) - log(Sum.W.2019$mean[1])
lrr.W.2019$var<-lrr.W.2019$sd^2/(lrr.W.2019$count*lrr.W.2019$mean^2) + Sum.W.2019$sd[1]^2/(Sum.W.2019$count[1]*Sum.W.2019$mean[1]^2)
lrr.W.2019$CI<-qnorm(0.975)*sqrt(lrr.W.2019$var)
lrr.W.2019$SE<-sqrt(lrr.W.2019$var)/sqrt(lrr.W.2019$count)
lrr.W.2019$CI_up <- lrr.W.2019$LRR+lrr.W.2019$CI
lrr.W.2019$CI_down <- lrr.W.2019$LRR-lrr.W.2019$CI
lrr.W.2019$Population <- "Wellspring Pond"

# Churchill 2020
Sum.C.2020 <- subset(df.C.2020, plt == "Y") %>% group_by(bac) %>% dplyr::summarize(mean = mean(Grt, na.rm=T), sd = sd(Grt, na.rm=T), count=n(),  sem = sd/sqrt(count))

lrr.C.2020<-Sum.C.2020[2:12,]
lrr.C.2020$LRR<-log(lrr.C.2020$mean) - log(Sum.C.2020$mean[1])
lrr.C.2020$var<-lrr.C.2020$sd^2/(lrr.C.2020$count*lrr.C.2020$mean^2) + Sum.C.2020$sd[1]^2/(Sum.C.2020$count[1]*Sum.C.2020$mean[1]^2)
lrr.C.2020$CI<-qnorm(0.975)*sqrt(lrr.C.2020$var)
lrr.C.2020$SE<-sqrt(lrr.C.2020$var)/sqrt(lrr.C.2020$count)
lrr.C.2020$CI_up <- lrr.C.2020$LRR+lrr.C.2020$CI
lrr.C.2020$CI_down <- lrr.C.2020$LRR-lrr.C.2020$CI
lrr.C.2020$Population <- "Churchill Marsh"

#Wellspring
Sum.W.2020 <- subset(df.W.2020, plt == "Y") %>% group_by(bac) %>% dplyr::summarize(mean = mean(Grt, na.rm=T), sd = sd(Grt, na.rm=T), count=n(),  sem = sd/sqrt(count))

lrr.W.2020<-Sum.W.2020[2:12,]
lrr.W.2020$LRR<-log(lrr.W.2020$mean) - log(Sum.W.2020$mean[1])
lrr.W.2020$var<-lrr.W.2020$sd^2/(lrr.W.2020$count*lrr.W.2020$mean^2) + Sum.W.2020$sd[1]^2/(Sum.W.2020$count[1]*Sum.W.2020$mean[1]^2)
lrr.W.2020$CI<-qnorm(0.975)*sqrt(lrr.W.2020$var)
lrr.W.2020$SE<-sqrt(lrr.W.2020$var)/sqrt(lrr.W.2020$count)
lrr.W.2020$CI_up <- lrr.W.2020$LRR+lrr.W.2020$CI
lrr.W.2020$CI_down <- lrr.W.2020$LRR-lrr.W.2020$CI
lrr.W.2020$Population <- "Wellspring Pond"

#Make 2020 table
lrr.2020 <- rbind(lrr.C.2020, lrr.W.2020)
colnames(lrr.2020)[[1]] <- "Bacterial strain"
colnames(lrr.2020)[[10]] <- "Upper bound"
colnames(lrr.2020)[[11]] <- "Lower bound"
table_2020 <- kbl(lrr.2020[,c(12,1,6, 11,10)], format="latex", digits=4, caption="List of bacteria used in 2020 experiments, with log response ratios (LRR) and the lower and upper bounds of 95\\% confidence intervals for their effects on \\textit{Lemna minor} growth", booktabs=T, longtable=T, linesep = c('', '', '', '', '', '', '', '', '', '', '\\hline'))
```

```{latex}
table_2020
```

```{r Tables}
#Make 2019 table
lrr.2019 <- rbind(lrr.C.2019, lrr.K.2019, lrr.W.2019)
colnames(lrr.2019)[[1]] <- "Bacterial strain"
colnames(lrr.2019)[[10]] <- "Upper bound"
colnames(lrr.2019)[[11]] <- "Lower bound"
table_2019 <- kbl(lrr.2019[,c(12,1,6, 11,10)], format="latex", digits=4, caption="List of bacteria used in 2019 experiments, with log response ratios (LRR) and the lower and upper bounds of 95\\% confidence intervals for their effects on \\textit{Lemna minor} growth", booktabs=T, longtable=T, linesep = c('', '', '', '', '', '', '', '', '', '', '\\hline'))
table_2019
```

```{r Duckweed growth figures}
pt_size = 3
ylimits = c(-0.4, 1.1)
lrr.2020$color <- ifelse(lrr.2020$`Bacterial strain` == "All 10 bacteria", "10-strain community", "Single strain")
zero_line <- "red3"
sum_line <- "green3"
mean_line <- "blue3"
dot_colors <- c("blue", "black")

#Churchill 2020
pred.C.2020.avg <-mean(lrr.C.2020$LRR[1:10])
pred.C.2020.sum <-sum(lrr.C.2020$LRR[1:10])

plot_C2020 <- ggplot(subset(lrr.2020, Population == "Churchill Marsh"), aes(y=mean,x=reorder(`Bacterial strain`, LRR), color=color))+
  geom_point(size=pt_size)+
  geom_errorbar(aes(x=reorder(`Bacterial strain`,LRR), ymin=mean-sem,ymax=mean+sem),width=0.5)+
  #geom_errorbar(aes(x=reorder(`Bacterial strain`,LRR), ymin=LRR-SE,ymax=LRR+SE),width=0.5)+
  #geom_errorbar(aes(x=reorder(`Bacterial strain`,LRR), ymin=`Lower bound`,ymax=`Upper bound`),width=0.5)+
  theme_cowplot()+
#  geom_hline(yintercept=0, linetype="dashed", color = zero_line,size=1)+
 # geom_hline(yintercept=pred.C.2020.avg, linetype="dashed", color = mean_line,size=1)+
 # geom_hline(yintercept=pred.C.2020.sum, linetype="dashed", color = sum_line,size=1)+
  xlab("Bacterial strain")+
  ggtitle("Churchill")+
  theme(axis.text.x=element_text(angle=90, vjust=0.5, hjust=1))+
   theme(legend.title = element_blank())+
#  scale_y_continuous(limits=ylimits)+
  scale_color_manual(values=dot_colors)+
  theme(legend.position = c(0.1, 0.9))
plot_C2020
#tmp <- lrr.2020[lrr.2020$Population == "Churchill Marsh", "Bacterial strain"]
plot_C2020_updated <- plot_C2020+scale_x_discrete(labels=c("*Flavobacterium succinicans* 1", "*Bosea massiliensis*", "*Aeromonas salmonicida*", "*Ohtaekwangia koreensis*", "*Flavobacterium succinicans* 2", "*Falsiroseomonas stagni*", "*Parasediminibacterium paludis*", "*Arcicella* sp.", "*Microbacterium oxydans*", "*Pseudomonas protogens*", "All 10 bacteria"))+
  theme(axis.text.x = ggtext::element_markdown())
plot_C2020_updated

#Wellspring 2020
pred.W.2020.avg <-mean(lrr.W.2020$LRR[1:10])
pred.W.2020.sum <-sum(lrr.W.2020$LRR[1:10])

plot_W2020 <- ggplot(subset(lrr.2020, Population == "Wellspring Pond"), aes(y=LRR,x=reorder(`Bacterial strain`, LRR), color=color))+
  geom_point(size=pt_size)+
  geom_errorbar(aes(x=reorder(`Bacterial strain`,LRR), ymin=LRR-SE,ymax=LRR+SE),width=0.5)+
  #geom_errorbar(aes(x=reorder(`Bacterial strain`,LRR), ymin=`Lower bound`,ymax=`Upper bound`),width=0.5)+
  theme_cowplot()+
  geom_hline(yintercept=0, linetype="dashed", color = zero_line, size=1)+
  geom_hline(yintercept=pred.W.2020.avg, linetype="dashed", color = mean_line,size=1)+
  geom_hline(yintercept=pred.W.2020.sum, linetype="dashed", color = sum_line,size=1)+
  xlab("Bacterial strain")+
  ggtitle("Wellspring")+
  theme(axis.text.x=element_text(angle=90, vjust=0.5, hjust=1))+
  theme(legend.title = element_blank())+
  scale_y_continuous(limits=ylimits)+
  scale_color_manual(values=dot_colors)+
  theme(legend.position="none")
plot_W2020
#tmp <- lrr.2020[lrr.2020$Population == "Wellspring Pond", "Bacterial strain"]
plot_W2020_updated <- plot_W2020+scale_x_discrete(labels=c("*Sphingomonas pituitosa* 1", "*Flaviflagellibacter deserti*", "*Rhizobium rosettiformans*", "*Rhizorhabdus wittichii* 1", "*Rhizobium capsici* 1", "*Pseudomonas protogens*", "*Rhizorhabdus wittichii* 2", "*Rhizobium capsici* 2", "*Sphingomonas pituitosa* 2", "All 10 bacteria", "*Fervidobacterium riparium*"))+
  theme(axis.text.x = ggtext::element_markdown())
plot_W2020_updated

plot_2020 <- plot_grid(plot_C2020_updated, plot_W2020_updated, labels="AUTO", align='h')
plot_2020
```


```{r}
#OK, let's get to plotting!

pred.C.2019<-mean(lrr.C.2019$LRR[1:10])

plot1.C1 <- ggplot(lrr.C.2019,aes(y=LRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=LRR-SE,ymax=LRR+SE),width=0.5)+geom_point(size=3)
plot1.C1 <- plot1.C1 + geom_hline(yintercept=pred.C.2019, linetype="dashed", color = "blue3",size=1)
plot1.C1 <- plot1.C1 + theme_classic() + ggtitle("Churchill, 2019") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot1.C1 <- plot1.C1 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot1.C1 <- plot1.C1 + theme(legend.position = "none")
plot1.C1 <- plot1.C1 + labs(x= element_blank()) 
plot1.C1 <- plot1.C1 + labs(y= element_blank())
plot1.C1 <- plot1.C1 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))
plot1.C1 <- plot1.C1 + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

#Kelso 2019

pred.K.2019<-mean(lrr.K.2019$LRR[1:10])

plot1.K1 <- ggplot(lrr.K.2019,aes(y=LRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=LRR-SE,ymax=LRR+SE),width=0.5)+geom_point(size=3)
plot1.K1 <- plot1.K1 + geom_hline(yintercept=pred.K.2019, linetype="dashed", color = "blue3",size=1)
plot1.K1 <- plot1.K1 + theme_classic() + ggtitle("Kelso, 2019") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot1.K1 <- plot1.K1 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot1.K1 <- plot1.K1 + theme(legend.position = "none")
plot1.K1 <- plot1.K1 + labs(x= element_blank()) 
plot1.K1 <- plot1.K1 + labs(y= element_blank())
plot1.K1 <- plot1.K1 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))
plot1.K1 <- plot1.K1 + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

#Wellspring 2019

pred.W.2019<-mean(lrr.W.2019$LRR[1:10])

plot1.W1 <- ggplot(lrr.W.2019,aes(y=LRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=LRR-SE,ymax=LRR+SE),width=0.5)+geom_point(size=3)
plot1.W1 <- plot1.W1 + geom_hline(yintercept=pred.W.2019, linetype="dashed", color = "blue3",size=1)
plot1.W1 <- plot1.W1 + theme_classic() + ggtitle("Wellspring, 2019") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot1.W1 <- plot1.W1 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot1.W1 <- plot1.W1 + theme(legend.position = "none")
plot1.W1 <- plot1.W1 + labs(x= element_blank()) 
plot1.W1 <- plot1.W1 + labs(y= element_blank())
plot1.W1 <- plot1.W1 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))
plot1.W1 <- plot1.W1 + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

# Churchill 2020

pred.C.2020<-mean(lrr.C.2020$LRR[1:10])

plot1.C2 <- ggplot(lrr.C.2020,aes(y=LRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=LRR-SE,ymax=LRR+SE),width=0.5)+geom_point(size=3)
plot1.C2 <- plot1.C2 + geom_hline(yintercept=pred.C.2020, linetype="dashed", color = "blue3",size=1)
plot1.C2 <- plot1.C2 + theme_classic() + ggtitle("Churchill, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot1.C2 <- plot1.C2 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot1.C2 <- plot1.C2 + theme(legend.position = "none")
plot1.C2 <- plot1.C2 + labs(x= element_blank()) 
plot1.C2 <- plot1.C2 + labs(y= element_blank())
plot1.C2 <- plot1.C2 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))
plot1.C2 <- plot1.C2 + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

# Wellspring 2020

pred.W.2020<-mean(lrr.W.2020$LRR[1:10])

plot1.W2 <- ggplot(lrr.W.2020,aes(y=LRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=LRR-SE,ymax=LRR+SE),width=0.5)+geom_point(size=3)
plot1.W2 <- plot1.W2 + geom_hline(yintercept=pred.W.2020, linetype="dashed", color = "blue3",size=1)
plot1.W2 <- plot1.W2 + theme_classic() + ggtitle("Wellspring, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot1.W2 <- plot1.W2 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot1.W2 <- plot1.W2 + theme(legend.position = "none")
plot1.W2 <- plot1.W2 + labs(x= element_blank()) 
plot1.W2 <- plot1.W2 + labs(y= element_blank())
plot1.W2 <- plot1.W2 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))
plot1.W2 <- plot1.W2 + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

#Legend plot
#Create dead column for individual bacteria
lrr.C.2019$legend.bac<-c(rep('Individual bacteria',10),'All 10 bacteria')
lrr.C.2019$legend.bac<-as.factor(lrr.C.2019$legend.bac)
factor(lrr.C.2019$legend.bac, levels = c("Individual bacteria","All 10 bacteria"))

lrr.C.2019$legend.line<-c(rep('No effect of inoculation',6),rep('Mean effect of individual bacteria',5))
lrr.C.2019$legend.line<-as.factor(lrr.C.2019$legend.line)

leg.plot <- ggplot(lrr.C.2019, aes(x = LRR, y = var, colour = legend.bac)) + geom_point(size=3)
leg.plot <- leg.plot + scale_colour_manual(name="Bacterial inocula",values=c("blue3","#000000"))
leg.plot <- leg.plot + theme_classic()
leg.plot <- leg.plot + theme(
  legend.title=element_text(size=14, face='bold'),
  legend.text=element_text(size=12, face='bold')
)

leg.1 <- get_legend(leg.plot)  

leg.plot.2 <- ggplot(lrr.C.2019, aes(x = LRR, y = var, colour = legend.line)) + geom_point(size=3) + geom_line(linetype="dashed",size=1)
leg.plot.2 <- leg.plot.2 + scale_colour_manual(name="Line",values=c("blue3","red3"))
leg.plot.2 <- leg.plot.2 + theme_classic() 
leg.plot.2 <- leg.plot.2 + theme(
  legend.title=element_text(size=14, face='bold'),
  legend.text=element_text(size=12, face='bold')
)

leg.2 <- get_legend(leg.plot.2)  

plot.leg<-plot_grid(leg.1, leg.2, ncol=1,nrow=2, align='v')

# Generate figure 1

x.grob_bac <- textGrob(expression(bold("Bacterial strain")), gp=gpar(fontsize=12))
y.grob_lrrdw <- textGrob(expression(bold("                     Duckweed growth (LRR)")), gp=gpar(fontsize=12), rot=90)

# Re-scale y axes
plot1.C1 <- plot1.C1 + ylim(-2.5,1)
plot1.K1 <- plot1.K1 + ylim(-2.5,1)
plot1.W1 <- plot1.W1 + ylim(-2.5,1)

plot1.C2 <- plot1.C2 + ylim(-0.2,0.4)
plot1.W2 <- plot1.W2 + ylim(-0.2,0.4)

plot1.2019<-plot_grid(plot1.C1, plot1.K1, plot1.W1, ncol=3,nrow=1, align='h', labels=c('A','B','C'))

plot1.2020<-plot_grid(plot1.C2, plot1.W2, plot.leg, ncol=3,nrow=1, align='h', labels=c('A','B'))


```



SECTION 4: Microbial growth models and figures

```{r Microbial growth models}
#Churchill 2020

# Model 1 : we will exclude control plants, and use All10_pltN as our reference treatment.
df.C.2020$bac2<-df.C.2020$bac
df.C.2020 <- within(df.C.2020, bac2 <- relevel(bac2, ref = 12))

lmer.abs.C<-lmer(logabs~bac2*plt + (1|edge) + (1|plate), data=df.C.2020)
anova(lmer.abs.C)
ranova(lmer.abs.C)
plot(lmer.abs.C)
summary(lmer.abs.C)

#Model 2 : we will exclude wells without plants to estimate variation in bacterial cell density when co-cultured with plants.
df.C.2020.plt<-subset(df.C.2020,df.C.2020$plt=="Y")
lmer.abs.C.2<-lmer(logabs~bac2 + (1|edge) + (1|plate), data=df.C.2020.plt)
summary(lmer.abs.C.2)

#Wellspring 2020

df.W.2020$bac2<-df.W.2020$bac
df.W.2020 <- within(df.W.2020, bac2 <- relevel(bac2, ref = 12))

lmer.abs.W<-lmer(logabs~bac2*plt + (1|edge) + (1|plate), data=df.W.2020)
anova(lmer.abs.W, type=3)
ranova(lmer.abs.W)
plot(lmer.abs.W)
summary(lmer.abs.W)

df.W.2020.plt<-subset(df.W.2020,df.W.2020$plt=="Y")
lmer.abs.W.2<-lmer(logabs~bac2 + (1|edge) + (1|plate), data=df.W.2020.plt)
summary(lmer.abs.W.2)

# Generate Figure 2

melt.C.abs<-melt(df.C.2020, id.vars=c("bac","plt"), measure.vars= "abs", na.rm = T)
Sum.C.abs<- ddply(melt.C.abs, c("bac","plt","variable"), summarise, mean = mean(value), sd = sd(value), count=n(), sem = sd(value)/sqrt(length(value)))

# Re-order by bacterial population size

Sum.C.abs$bac <- factor(Sum.C.abs$bac, levels = c("Control","Microbacterium \noxydans","Bosea \nmassiliensis","Flavobacterium \nsuccinicans 1","Falsiroseomonas \nstagni","Ohtaekwangia \nkoreensis","Flavobacterium \nsuccinicans 2","Aeromonas \nsalmonicida","Arcicella sp.","Parasediminibacterium \npaludis","Pseudomonas \nprotogens","All 10 bacteria"))
Sum.C.abs$CI<-qnorm(0.975)*Sum.C.abs$sd/sqrt(Sum.C.abs$count)

Sum.C.plt<-subset(Sum.C.abs, Sum.C.abs$plt=="Y")
Sum.C.plt<-Sum.C.plt[2:12,]
Sum.C.plt$CI<-qnorm(0.975)*Sum.C.plt$sd/sqrt(Sum.C.plt$count)

Sum.C.bac<-subset(Sum.C.abs, Sum.C.abs$plt=="N")
Sum.C.bac$CI<-qnorm(0.975)*Sum.C.bac$sd/sqrt(Sum.C.bac$count)

pred.C.plt<-mean(Sum.C.plt$mean[1:10])
pred.C.bac<-mean(Sum.C.bac$mean[1:10])

plot2.C1 <- ggplot(Sum.C.bac,aes(y=mean,x=bac,colour=bac))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5)+geom_point(size=3)
plot2.C1 <- plot2.C1 + geom_hline(yintercept=pred.C.bac, linetype="dashed", color = "blue3",size=1)
plot2.C1 <- plot2.C1 + theme_classic() + ggtitle("Churchill, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot2.C1 <- plot2.C1 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot2.C1 <- plot2.C1 + theme(legend.position = "none")
plot2.C1 <- plot2.C1 + labs(x= element_blank()) 
plot2.C1 <- plot2.C1 + labs(y= element_blank())
plot2.C1 <- plot2.C1 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))

plot2.C2 <- ggplot(Sum.C.plt,aes(y=mean,x=bac,colour=bac))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5)+geom_point(size=3)
plot2.C2 <- plot2.C2 + geom_hline(yintercept=pred.C.plt, linetype="dashed", color = "blue3",size=1)
plot2.C2 <- plot2.C2 + theme_classic() + ggtitle("Churchill, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot2.C2 <- plot2.C2 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot2.C2 <- plot2.C2 + theme(legend.position = "none")
plot2.C2 <- plot2.C2 + labs(x= element_blank()) 
plot2.C2 <- plot2.C2 + labs(y= element_blank())
plot2.C2 <- plot2.C2 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))

#Wellspring

melt.W.abs<-melt(df.W.2020, id.vars=c("bac","plt"), measure.vars= "abs", na.rm = T)
Sum.W.abs<- ddply(melt.W.abs, c("bac","plt","variable"), summarise,
                mean = mean(value), sd = sd(value), count=n(),
                sem = sd(value)/sqrt(length(value)))

Sum.W.abs$bac <- factor(Sum.W.abs$bac, levels = c("Control","Flaviflagellibacter \ndeserti","Rhizorhabdus \nwittichii 2","Rhizorhabdus \nwittichii 1","Rhizobium \ncapsici 2","Rhizobium \ncapsici 1","Sphingomonas \npituitosa 2","Sphingomonas \npituitosa 1","Fervidobacterium \nriparium","Rhizobium \nrosettiformans","Pseudomonas \nprotogens","All 10 bacteria"))
Sum.W.abs$CI<-qnorm(0.975)*Sum.W.abs$sd/sqrt(Sum.W.abs$count)

Sum.W.plt<-subset(Sum.W.abs, Sum.W.abs$plt=="Y")
Sum.W.plt<-Sum.W.plt[2:12,]
Sum.W.plt$CI<-qnorm(0.975)*Sum.W.plt$sd/sqrt(Sum.W.plt$count)

Sum.W.bac<-subset(Sum.W.abs, Sum.W.abs$plt=="N")
Sum.W.bac$CI<-qnorm(0.975)*Sum.W.bac$sd/sqrt(Sum.W.bac$count)

pred.W.plt<-mean(Sum.W.plt$mean[1:10])
pred.W.bac<-mean(Sum.W.bac$mean[1:10])

plot2.W1 <- ggplot(Sum.W.bac,aes(y=mean,x=bac,colour=bac))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5)+geom_point(size=3)
plot2.W1 <- plot2.W1 + geom_hline(yintercept=pred.W.bac, linetype="dashed", color = "blue3",size=1)
plot2.W1 <- plot2.W1 + theme_classic() + ggtitle("Wellspring, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot2.W1 <- plot2.W1 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot2.W1 <- plot2.W1 + theme(legend.position = "none")
plot2.W1 <- plot2.W1 + labs(x= element_blank()) 
plot2.W1 <- plot2.W1 + labs(y= element_blank())
plot2.W1 <- plot2.W1 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))

plot2.W2 <- ggplot(Sum.W.plt,aes(y=mean,x=bac,colour=bac))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5)+geom_point(size=3)
plot2.W2 <- plot2.W2 + geom_hline(yintercept=pred.W.plt, linetype="dashed", color = "blue3",size=1)
plot2.W2 <- plot2.W2 + theme_classic() + ggtitle("Wellspring, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot2.W2 <- plot2.W2 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot2.W2 <- plot2.W2 + theme(legend.position = "none")
plot2.W2 <- plot2.W2 + labs(x= element_blank()) 
plot2.W2 <- plot2.W2 + labs(y= element_blank())
plot2.W2 <- plot2.W2 + theme(axis.text.x = element_text(face="italic",angle = 90,vjust=0.5,hjust=1))

# Re-scale y axes
plot2.C1 <- plot2.C1 + ylim(0,11000)
plot2.W1 <- plot2.W1 + ylim(0,11000)

plot2.C2 <- plot2.C2 + ylim(0,10500)
plot2.W2 <- plot2.W2 + ylim(0,10500)

#OK, now we need to combine them both and make a reaction norm plot.

Sum.C.abs2 <- Sum.C.abs[2:23,]

plot2.C3 <- ggplot(Sum.C.abs2, aes(x = plt, y = mean, colour=bac)) +  stat_summary(aes(group = bac), fun = mean, geom = "path") +geom_point(size=3)
plot2.C3 <- plot2.C3 + theme_classic() + ggtitle("Churchill, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot2.C3 <- plot2.C3 + labs(x= element_blank())
plot2.C3 <- plot2.C3 + labs(y= element_blank())
plot2.C3 <- plot2.C3 + theme(axis.title = element_text(face="bold", size=12))
plot2.C3 <- plot2.C3 + scale_x_discrete(labels=c("N" = "No duckweed", "Y" = "Duckweed"))
plot2.C3 <- plot2.C3 + theme(axis.text.x = element_text(face="bold",size = 12, colour="black"))
plot2.C3 <- plot2.C3 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot2.C3 <- plot2.C3 + theme(legend.position = "none")

Sum.W.abs2 <- Sum.W.abs[2:23,]

plot2.W3 <- ggplot(Sum.W.abs2, aes(x = plt, y = mean, colour=bac)) +  stat_summary(aes(group = bac), fun = mean, geom = "path") +geom_point(size=3)
plot2.W3 <- plot2.W3 + theme_classic() + ggtitle("Wellspring, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot2.W3 <- plot2.W3 + labs(x= element_blank())
plot2.W3 <- plot2.W3 + labs(y= element_blank())
plot2.W3 <- plot2.W3 + theme(axis.title = element_text(face="bold", size=12))
plot2.W3 <- plot2.W3 + scale_x_discrete(labels=c("N" = "No duckweed", "Y" = "Duckweed"))
plot2.W3 <- plot2.W3 + theme(axis.text.x = element_text(face="bold",size = 12, colour="black"))
plot2.W3 <- plot2.W3 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot2.W3 <- plot2.W3 + theme(legend.position = "none")

plot2.bac1<-plot_grid(plot2.C1, plot2.C2, plot2.C3, ncol=3,nrow=1, align='h', labels = c('A','B','C'))
plot2.bac2<-plot_grid(plot2.W1, plot2.W2, plot2.W3, ncol=3,nrow=1, align='h', labels = c('D','E','F'))

plot2.1<-plot_grid(plot2.bac1,plot2.bac2, nrow = 2, ncol=1, align='v')

y.grob_abs <- textGrob(expression(bold("                       Microbial density (cells/µL)")), gp=gpar(fontsize=12), rot=90)

x.grob_bac2 <- textGrob(expression(bold("Bacteria                                                                     ")), gp=gpar(fontsize=12))

x.grob.plt <- textGrob(expression(bold("No plants                                                                             Plants                                                                                ")), gp=gpar(fontsize=12))

grid.arrange(arrangeGrob(plot2.1, left = y.grob_abs, bottom = x.grob_bac2, top=x.grob.plt))

#Let's arrange it the other way too.

plot2.C1b <- plot2.C1 + labs(y= "No plants") 
plot2.C1b <- plot2.C1b + theme(axis.title = element_text(size=12, face='bold'))

plot2.C2b <- plot2.C2 + labs(y= "Plants") 
plot2.C2b <- plot2.C2b + theme(axis.title = element_text(size=12, face='bold'))

plot2.bac1b<-plot_grid(plot2.C1b, plot2.W1, plot2.C3, ncol=3,nrow=1, align='h', labels = c('A','B','E'))
plot2.bac2b<-plot_grid(plot2.C2b, plot2.W2, plot2.W3, ncol=3,nrow=1, align='h', labels = c('C','D','F'))

plot2.2<-plot_grid(plot2.bac1b,plot2.bac2b, nrow = 2, ncol=1, align='v')

grid.arrange(arrangeGrob(plot2.2, left = y.grob_abs, bottom = x.grob_bac2))

```

SECTION 5: Fitness regression

```{r Fitness regression}

# We will fit models (with full random effect structure) from which we can extract 'genotype' (i.e. bacterial inocula) means for their (1) effects on duckweed growth, and (2) microbial density when grown with plants.
# We will use scaled data so that we can center fitness proxy data around 0.

df.C.fit<-subset(df.C.2020, df.C.2020$bac!="Control" & df.C.2020$plt=="Y")
df.C.fit$Grt.scaled<-(df.C.fit$Grt-mean(df.C.fit$Grt,na.rm=T))/sd(df.C.fit$Grt,na.rm=T)
df.C.fit$pix0.scaled<-(df.C.fit$pix0-mean(df.C.fit$pix0,na.rm=T))/sd(df.C.fit$pix0,na.rm=T)
df.C.fit$abs.scaled<-(df.C.fit$abs-mean(df.C.fit$abs,na.rm=T))/sd(df.C.fit$abs,na.rm=T)

# Now we create models that we can extract strain/genotype means from
modC.grt<-lmer(Grt.scaled ~ bac + pix0.scaled + (1|edge) +(1|plate), data=df.C.fit)
em.C.grt<-as.data.frame(emmeans(modC.grt, "bac", var="Grt.scaled"))
em.C.grt$CI<-em.C.grt$SE*qnorm(0.975)

modC.abs<-lmer(abs.scaled ~ bac + (1|edge) +(1|plate), data=df.C.fit)
em.C.abs<-as.data.frame(emmeans(modC.abs, "bac", var="abs.scaled"))
em.C.abs$CI<-em.C.abs$SE*qnorm(0.975)

em.C.grt$abs<-em.C.abs$emmean
em.C.grt$abs.CI<-em.C.abs$CI
em.C.grt$abs.SE<-em.C.abs$SE

em.C.grt$num<-1:11

# Is there a significant correlation between bacterial cell density and duckweed growth?
regC<-lm(emmean~abs,data=em.C.grt)
summary(regC)

plot3.C1 <- ggplot(em.C.grt, aes(x = abs, y = emmean, colour = bac, fill=bac)) + geom_point(size=3,key_glyph=draw_key_blank) + geom_pointrange(aes(ymin=emmean-SE,ymax=emmean+SE),key_glyph=draw_key_blank) + geom_pointrange(aes(xmin=abs-abs.SE, xmax=abs+abs.SE),key_glyph=draw_key_blank)
plot3.C1 <- plot3.C1 + theme_classic() + ggtitle("Churchill, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot3.C1 <- plot3.C1 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot3.C1 <- plot3.C1 + labs(x= element_blank())
plot3.C1 <- plot3.C1 + labs(y= "Duckweed growth")
plot3.C1 <- plot3.C1 + theme(axis.title = element_text(face="bold", size=12))
plot3.C1 <- plot3.C1 + geom_text_repel(aes(label = num), point.padding = 0.25, box.padding =0.25, fontface="bold", show.legend = FALSE)
plot3.C1 <- plot3.C1 + theme(legend.title=element_blank())
plot3.C1 <- plot3.C1 + scale_fill_discrete(labels = c(
  substitute(paste(bold("1 "), bolditalic("Flavobacterium succinicans "),bold("1"))), 
  substitute(paste(bold("2 "), bolditalic("Bosea massiliensis"))),
  substitute(paste(bold("3 "), bolditalic("Aeromonas salmonicida"))), 
  substitute(paste(bold("4 "), bolditalic("Ohtaekwangia koreensis"))), 
  substitute(paste(bold("5 "), bolditalic("Flavobacterium succinicans "),bold("2"))),
  substitute(paste(bold("6 "), bolditalic("Falsiroseomonas stagni"))), 
  substitute(paste(bold("7 "), bolditalic("Parasediminibacterium paludis"))), 
  substitute(paste(bold("8 "), bolditalic("Arcicella "), bold("sp."))), 
  substitute(paste(bold("9 "), bolditalic("Microbacterium oxydans"))), 
  substitute(paste(bold("10 "), bolditalic("Pseudomonas protogens"))),
  substitute(paste(bold("11 "), bold("All 10 bacteria")))
))
plot3.C1 <- plot3.C1 + guides(colour = FALSE)

df.W.fit<-subset(df.W.2020, df.W.2020$bac!="Control" & df.W.2020$plt=="Y")
df.W.fit$Grt.scaled<-(df.W.fit$Grt-mean(df.W.fit$Grt,na.rm=T))/sd(df.W.fit$Grt,na.rm=T)
df.W.fit$pix0.scaled<-(df.W.fit$pix0-mean(df.W.fit$pix0,na.rm=T))/sd(df.W.fit$pix0,na.rm=T)
df.W.fit$abs.scaled<-(df.W.fit$abs-mean(df.W.fit$abs,na.rm=T))/sd(df.W.fit$abs,na.rm=T)

modW.grt<-lmer(Grt.scaled ~ bac + pix0.scaled + (1|edge) +(1|plate), data=df.W.fit)
em.W.grt<-as.data.frame(emmeans(modW.grt, "bac", var="Grt.scaled"))
em.W.grt$CI<-em.W.grt$SE*qnorm(0.975)

modW.abs<-lmer(abs.scaled ~ bac + (1|edge) +(1|plate), data=df.W.fit)
em.W.abs<-as.data.frame(emmeans(modW.abs, "bac", var="abs.scaled"))
em.W.abs$CI<-em.W.abs$SE*qnorm(0.975)

em.W.grt$abs<-em.W.abs$emmean
em.W.grt$abs.CI<-em.W.abs$CI
em.W.grt$abs.SE<-em.W.abs$SE
em.W.grt$num<-1:11

# Is there a significant correlation between bacterial cell density and duckweed growth?
regW<-lm(emmean~abs,data=em.W.grt)
summary(regW)

plot3.W1 <- ggplot(em.W.grt, aes(x = abs, y = emmean, colour = bac, fill=bac)) + geom_point(size=3,key_glyph=draw_key_blank) + geom_pointrange(aes(ymin=emmean-SE,ymax=emmean+SE),key_glyph=draw_key_blank) + geom_pointrange(aes(xmin=abs-abs.SE, xmax=abs+abs.SE),key_glyph=draw_key_blank)
plot3.W1 <- plot3.W1 + theme_classic() + ggtitle("Wellspring, 2020") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
plot3.W1 <- plot3.W1 + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
plot3.W1 <- plot3.W1 + labs(x= element_blank())
plot3.W1 <- plot3.W1 + labs(y= element_blank())
plot3.W1 <- plot3.W1 + theme(axis.title = element_text(face="bold", size=12))
plot3.W1 <- plot3.W1 + geom_text_repel(aes(label = num), point.padding = 0.25, box.padding =0.25, fontface="bold", show.legend = FALSE)
plot3.W1 <- plot3.W1 + theme(legend.title=element_blank())
plot3.W1 <- plot3.W1 + scale_fill_discrete(labels = c(
  substitute(paste(bold("1 "), bolditalic("Sphingomonas pituitosa "), bold("1"))), 
  substitute(paste(bold("2 "), bolditalic("Flaviflagellibacter deserti"))),
  substitute(paste(bold("3 "), bolditalic("Rhizobium rosettiformans"))), 
  substitute(paste(bold("4 "), bolditalic("Rhizorhabdus wittichii "), bold("1"))), 
  substitute(paste(bold("5 "), bolditalic("Rhizobium capsici "), bold("1"))),
  substitute(paste(bold("6 "), bolditalic("Pseudomonas protogens"))), 
  substitute(paste(bold("7 "), bolditalic("Rhizorhabdus wittichii "), bold("2"))), 
  substitute(paste(bold("8 "), bolditalic("Rhizobium capsici "), bold("2"))),
  substitute(paste(bold("9 "), bolditalic("Sphingomonas pituitosa "), bold("2"))),
  substitute(paste(bold("10 "), bolditalic("Fervidobacterium riparium"))),
  substitute(paste(bold("11 "), bold("All 10 bacteria")))
))
plot3.W1 <- plot3.W1 + guides(colour = FALSE)

# Re-scale axes?
#plot3.C1 <- plot3.C1 + ylim(-0.75,1)
#plot3.W1 <- plot3.W1 + ylim(-0.75,1)
#plot3.C1 <- plot3.C1 + xlim(-1.5,3)
#plot3.W1 <- plot3.W1 + xlim(-1.5,3)

plot3<-plot_grid(plot3.C1, plot3.W1, ncol=2,nrow=1, align='h', labels = c('A','B'))

x.grob_abs <- textGrob(expression(bold("Microbial density")), gp=gpar(fontsize=12))
grid.arrange(arrangeGrob(plot3, bottom = x.grob_abs))

# 15 x 5?

```
