---
title: "Data_analysis"
author: "Jason Laurich"
date: '2022-09-28'
output: 
  html_document: 
    keep_md: true
---

This file will analyse data pertaining to all Lemna minor single and mixed inoculation trials. We will generate figures and do some modelling.

SECTION 1: Upload packages

```{r Packages, message=FALSE, warning=FALSE}
library(ggplot2) # we need this for plotting
library(reshape2) # melting and stuff
library(plyr) # manipulating data frames
library(dplyr)
library(car) # type 3 anovas
library(lme4) # mixed effects models
library(emmeans) # allows extraction of bacteria-specific regression estimates.
library(RLRsim) # test significance of random effects
library(cowplot) # make plot grids
library(grid)
library(gridExtra) # adjust and manipulate combined plots. 
```

SECTION 2: Upload data for the latest round of experiments

```{r Data, message=FALSE, warning=FALSE}
setwd("C:/Users/jason/Dropbox/My PC (DESKTOP-IOO274E)/Desktop/Data/Lemna_singleinoculations/Lemna_single_inoculations")

df<-read.table('CW_mixed_inoculation_data.txt', header=F, na.strings="", sep="\t")
names(df)<-c('pop','plt','bac','id','frd0','pix0','per0','grn0','grnper0','frd1','pix1','per1','grn1','grnper1','abs')
str(df)

#Fix the structure for bacterial inoculation and plant
df$bac <- factor(df$bac, levels = c("Control", "1", "2", "3", "4", "5","6","7","8","9","10","All10"))
df$plt <- as.factor(df$plt)

# Need to add in edge effects. So for each 24 well plate, all but 6,7,10,11,14,15,18, and 19 are edge.
edge<-c(rep("Y",5), rep("N",2), rep("Y",2),rep("N",2), rep("Y",2), rep("N",2), rep("Y",2),rep("N",2), rep("Y",5))

edge2<-rep(edge,38)
edge2<-c(edge2, rep("Y",5), rep("N",2), "Y")
df$edge<-edge2

df$edge <- as.factor(df$edge)

#Take out errors (pipetting errors, wrong bacteria)
df<-df[-c(453,494,798),]

#Let's generate some summary statistics. Things like greenness (health), growth (fitness), and aggregation.

df$Grt<-df$pix1 - df$pix0
df$Agg<-df$pix1/df$per1
df$Hlth<-df$grn1/df$pix1

#Let's check the normality of our data
ggplot(data=df, aes(x = Grt)) + geom_histogram(fill = "white", colour = "black")
# Looks pretty good

ggplot(data=df, aes(x = Agg)) + geom_histogram(fill = "white", colour = "black")
# Looks pretty good

ggplot(data=df, aes(x = Hlth)) + geom_histogram(fill = "white", colour = "black")
# Looks pretty good

#What about bacterial fitness data? Let's look at absolute count.
ggplot(data=df, aes(x = abs)) + geom_histogram(fill = "white", colour = "black")
# Right-tailed, heavily.
ggplot(data=df, aes(x = abs)) + geom_histogram(fill = "white", colour = "black") +  facet_grid(pop ~ plt, scales = "free")
# That looks better — most of the low values come from wells lacking plants. 

# Let's create a logged absolute count column anyway
df$logabs<-log(df$abs)

ggplot(data=df, aes(x = logabs)) + geom_histogram(fill = "white", colour = "black") +  facet_grid(pop ~ plt, scales = "free")
# That looks better still!

#Let's create separate dataframes for each population
dfC<-subset(df, df$pop== "Churchill")
dfW<-subset(df, df$pop== "Wellspring")

# Change factor order of bacteria to reflect their effects on duckweed growth.
#First, let's change the order of bacteria, ranked by effect. 
dfC$bac<- factor(dfC$bac, levels = c("Control","1","8","6","3","7","10","9","4","5","2","All10"))
# Assign names from sequencing
levels(dfC$bac) <- c("Control","Uncultured bacterium","Bosea sp.","Aeromonas salmonicida","Unknown1","Unknown2","Roseomonas sp.","Unknown3","Unknown4","Microbacterium sp.","Pseudomonas protogens","All 10 bacteria")

dfW$bac<- factor(dfW$bac, levels = c("Control","2","8","1","9","6","3","5","4","7","10","All10"))
levels(dfW$bac) <- c("Control","Sphingomonas sp. 1","Rhizobiales sp.","Rhizobium sp. 1","Rhizorhabdus phycospaerae 1","Unknown1","Pseudomonas protogens","Rhizorhabdus phycosphaerae 2","Rhizobium sp. 2","Sphingomonas sp. 2","Pseudomonas aeruginosa","All 10 bacteria")

#Generate summary statistics.

melt_LRRC<-melt(dfC, id.vars=c("bac"), measure.vars= "Grt", na.rm = T)
Sum_LRRC<- ddply(melt_LRRC, c("bac","variable"), summarise,
      mean = mean(value), sd = sd(value), count=n(),
      sem = sd(value)/sqrt(length(value)))

lrrC<-data.frame(matrix(ncol=4, nrow=11))
names(lrrC)<-c('bac','LRR','var','SE')

lrrC$bac<-Sum_LRRC$bac[2:12]

#Reference for calculating LRR's: Hedges, L. V., Gurevitch, J., & Curtis, P. S. (1999). The meta-analysis of response ratios in experimental ecology. Ecology, 80(4), 1150-1156. Equation 1

for (i in 1:11){
  lrrC[i,2]<-log(Sum_LRRC[i+1,3]/Sum_LRRC[1,3])
  lrrC[i,3]<-Sum_LRRC[i+1,4]^2/(Sum_LRRC[i+1,5]*Sum_LRRC[i+1,3]^2) + Sum_LRRC[1,5]^2/(Sum_LRRC[1,6]*Sum_LRRC[1,4]^2)
}

lrrC$SE<-sqrt(lrrC$var)

#Wellspring
melt_LRRW<-melt(dfW, id.vars=c("bac"), measure.vars= "Grt", na.rm = T)
Sum_LRRW<- ddply(melt_LRRW, c("bac","variable"), summarise,
      mean = mean(value), sd = sd(value), count=n(),
      sem = sd(value)/sqrt(length(value)))

lrrW<-data.frame(matrix(ncol=4, nrow=11))
names(lrrW)<-c('bac','LRR','var','SE')

lrrW$bac<-Sum_LRRW$bac[2:12]

for (i in 1:11){
  lrrW[i,2]<-log(Sum_LRRW[i+1,3]/Sum_LRRW[1,3])
  lrrW[i,3]<-Sum_LRRW[i+1,4]^2/(Sum_LRRW[i+1,5]*Sum_LRRW[i+1,3]^2) + Sum_LRRW[1,5]^2/(Sum_LRRW[1,6]*Sum_LRRW[1,4]^2)
}

lrrW$SE<-sqrt(lrrW$var)
```

SECTION 3: Churchill: Modelling.

```{r Churchill models}

#How does bacterial inoculation affect growth?
modC_Grt<-lm(Grt~bac,data=dfC)
anova(modC_Grt)
summary(modC_Grt)
#not quite significant, but all 10 bacteria and P. protogens are significantly different from the mean. 

#What if we look at initial and final pixel count variation?
modC_pix<-lm(pix1~bac+pix0,data=dfC)
Anova(modC_pix, type=3)
summary(modC_pix)
#So it seems like the starting pixel count has a highly significant effect on eventual biomass. If you account for this, bacteria comes out as significant.
#All 10 and P.p still sig

# Let's add in edge effects.
modC_pixgrt<-lm(pix1~bac+pix0+edge,data=dfC)
Anova(modC_pixgrt, type=3)
summary(modC_pixgrt)
#So edge is significant, and its inclusion retains all other results.

#Let's try that as a random effect
lmer.grt<-lmer(pix1~pix0 + bac +(1|edge),data=dfC)
summary(lmer.grt)
Anova(lmer.grt, type=3)

exactRLRT(lmer.grt)
#So, yeah...

#How does bacterial identity and the presence of plants affect cell density?
modC_abs<-lm(logabs~bac*plt+edge,data=dfC)
anova(modC_abs)
summary(modC_abs)
#so bacterial identity, plant presence, and the interaction between them all matter here.

#What do the models say?
regC<-lm(Grt~logabs+bac+edge,data=dfC)
Anova(regC, type = 3)
summary(regC)

regC2<-lm(pix1~logabs+pix0+bac+edge,data=dfC)
Anova(regC2, type = 3)
summary(regC2)
#So regardless of how we measure growth rate, bacterial identity (fixed effect) and logged absolute count are correlated with duckweed fitness. Edge too. 

#What about an interaction term? This will set up emmeans analysis too. 
regC3<-lm(Grt~logabs*bac+edge,data=dfC)
Anova(regC3, type = 3)
summary(regC3)
#Only interaction term comes out as NEARLY significant. Power?

regC4<-lm(pix1~logabs*bac + pix0+edge,data=dfC)
Anova(regC4, type = 3)
summary(regC4)
#hmm... not much

# So we know (1) there is a relationship between bacterial and DW fitness that is positive and (2) bacterial identity affect duckweed fitness AND bacterial fitness, BUT (3) no interaction between b/w bacterial ID and absolute count can be pulled out here.

```

SECTION 4: Churchill: Plotting.

```{r Churchill plots}
# Let's plot!

dwC <- ggplot(Sum_LRRC,aes(y=mean,x=bac,colour=bac))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5)+geom_point(size=4.5)
dwC <- dwC + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
dwC <- dwC + scale_colour_manual(values=c("red3","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
dwC <- dwC + theme(legend.title=element_blank())
dwC <- dwC + theme(legend.position = "none")
dwC <- dwC + labs(x= element_blank()) 
dwC <- dwC + labs(y= "Duckweed growth (change in pixel count)")
dwC <- dwC + geom_hline(yintercept=15560.8, linetype="dashed", color = "red3",size=1)
dwC <- dwC + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))
dwC <- dwC + theme(axis.title = element_text(face="bold", size=12))

#OK, we want to add a line based on additive interactive effects among bacteria
#Calculate the effect of each microbe on plant growth
base_grtC<-Sum_LRRC[1,3]
Sum_LRRC$bac_eff<-(Sum_LRRC$mean - base_grtC)/10
add_predC<-sum(Sum_LRRC$bac_eff[2:12]) +base_grtC

dwC <- dwC + geom_hline(yintercept=add_predC, linetype="dashed", color = "blue3",size=1)

#Alright, let's plot LogRRs.

logC_plt <- ggplot(lrrC,aes(y=LRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=LRR-SE,ymax=LRR+SE),width=0.5)+geom_point(size=4.5)
logC_plt <- logC_plt + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
logC_plt <- logC_plt + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
logC_plt <- logC_plt + theme(legend.title=element_blank())
logC_plt <- logC_plt + theme(legend.position = "none")
logC_plt <- logC_plt + labs(x= element_blank()) 
logC_plt <- logC_plt + labs(y= "Effect size of bacterial inoculation (Log Response Ratio)")
logC_plt <- logC_plt + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))
logC_plt <- logC_plt + theme(axis.title = element_text(face="bold", size=12))
logC_plt <- logC_plt + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

# OK, let's look at bacteria.
# We need to generate some log rrs here too. Add to lrrC

#Generate summary estimates of bacterial abundance, with plant presence and absence 
melt_C_abs<-melt(dfC, id.vars=c("bac","plt"), measure.vars= "logabs", na.rm = T)
Sum_C_abs<- ddply(melt_C_abs, c("bac","plt","variable"), summarise,
                mean = mean(value), sd = sd(value), count=n(),
                sem = sd(value)/sqrt(length(value)))

for (i in 1:11){
  a<-i*2
  lrrC[i,5]<-log(Sum_C_abs[a+1,4]/Sum_C_abs[a,4])
  lrrC[i,6]<-Sum_C_abs[a+1,5]^2/(Sum_C_abs[a+1,6]*Sum_C_abs[a+1,4]^2) + Sum_C_abs[a,5]^2/(Sum_C_abs[1,6]*Sum_C_abs[1,4]^2)
}

names(lrrC)<-c('bac','LRR','var','SE','absLRR','absvar')
lrrC$absSE<-sqrt(lrrC$absvar)

absC <- ggplot(Sum_C_abs,aes(y=mean,x=bac,colour=bac,shape=plt))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5, position=position_dodge(width=0.4)) +geom_point(position=position_dodge(width=0.4), size=4.5)
absC <- absC + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
absC <- absC + scale_colour_manual(values=c("red3","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
absC <- absC + theme(legend.title=element_blank())
absC <- absC + guides(colour='none')
absC <- absC + scale_shape_discrete(name = "Treatment", labels = c("Bacteria only", "Plants & Bacteria"))
absC <- absC + theme(legend.position = c(0.7,0.9))
absC <- absC + labs(x= element_blank()) 
absC <- absC + labs(y= "Logged bacterial cell density (cells/µL)")
absC <- absC + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))
absC <- absC + theme(axis.title = element_text(face="bold", size=12))

#Let's collapse this to LogRR's? This plot would show the importance of plant presence to each bacteria

LRR_absC <- ggplot(lrrC,aes(y=absLRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=absLRR-absSE,ymax=absLRR+absSE),width=0.5, position=position_dodge(width=0.4)) +geom_point(position=position_dodge(width=0.4), size=4.5)
LRR_absC <- LRR_absC + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
LRR_absC <- LRR_absC + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
LRR_absC <- LRR_absC + guides(colour='none')
LRR_absC <- LRR_absC + theme(legend.title=element_blank())
LRR_absC <- LRR_absC + theme(legend.title=element_blank())
LRR_absC <- LRR_absC + labs(x= element_blank()) 
LRR_absC <- LRR_absC + labs(y= "Effect of plant presence (Log Response Ratio)")
LRR_absC <- LRR_absC + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))
LRR_absC <- LRR_absC + theme(axis.title = element_text(face="bold", size=12))
LRR_absC <- LRR_absC + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

# Then we can look at fitness regressions?
# Let's start by just graphing bacterial cell count against the growth rate of plants. This will ask the question "are the fitness estimates of bacteria and plants aligned? Are they broadly mutualistic?"

# Let's plot the raw regression first?
#Let's try plotting that with the full dataset, not the summary stats
regC <- ggplot(dfC,aes(y=logabs,x=Grt))+ geom_point()
regC <- regC + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regC <- regC + stat_smooth(method='lm',fullrange=F, se=T, size=2)
regC <- regC + labs(y= "Logged bacterial cell density (cells/µL)")
regC <- regC + labs(x= element_blank()) 
regC <- regC + theme(axis.title = element_text(face="bold", size=12))

# Let's plot the summary statistics. 
# Here, we want the mean absorbance for wells with plants ONLY
dfC.plt<-subset(dfC, dfC$plt=='Y')

melt_C_abs.plt<-melt(dfC.plt, id.vars=c("bac"), measure.vars= "logabs", na.rm = T)
Sum_C_abs.plt<- ddply(melt_C_abs, c("bac","variable"), summarise,
                mean = mean(value), sd = sd(value), count=n(),
                sem = sd(value)/sqrt(length(value)))

Sum_LRRC$mean.abs<- Sum_C_abs.plt$mean
Sum_LRRC$se.abs<- Sum_C_abs.plt$sem
  
regC2 <- ggplot(Sum_LRRC,aes(x=mean,y=mean.abs,colour=bac))+geom_errorbar(aes(xmin=mean-sem,xmax=mean+sem)) +geom_point(size=4.5)
regC2 <- regC2 + geom_errorbar(aes(ymin=mean.abs-se.abs,ymax=mean.abs+se.abs))
regC2 <- regC2 + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regC2 <- regC2 + scale_colour_manual(values=c("red3","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
regC2 <- regC2 + theme(legend.title=element_blank())
regC2 <- regC2 + theme(legend.position = "none")
regC2 <- regC2 + labs(x= element_blank()) 
regC2 <- regC2 + labs(y= "Logged bacterial cell density (cells/µL)")
regC2 <- regC2 + theme(axis.title = element_text(face="bold", size=12))

# Let's try the LogRR's
regClRR <- ggplot(lrrC,aes(y=absLRR,x=LRR,colour=bac))+ geom_point()
regClRR <- regClRR + geom_errorbar(aes(ymin=absLRR-absSE,ymax=absLRR+absSE))
regClRR <- regClRR + geom_errorbar(aes(xmin=LRR-SE, xmax=LRR+SE))
regClRR <- regClRR + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regClRR <- regClRR + theme(legend.title=element_blank())
regClRR <- regClRR + theme(legend.position = "none")
regClRR <- regClRR + labs(x= element_blank())  
regClRR <- regClRR + labs(y= "Effect size of plant presence (Log Response Ratio)")
regClRR <- regClRR + theme(axis.title = element_text(face="bold", size=12))
regClRR <- regClRR + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))

# Finally, let's plot fitness alignment (or estimate?) for each bacteria separately, and look at this?
# How about emtrends~ LogRR's (effects on plants)? Are more beneficial bacterial also more closely aligned?

# Let's ask that by plotting raw data for each bacteria
regC.bac <- ggplot(dfC,aes(y=logabs,x=Grt))+ geom_point()
regC.bac <- regC.bac + facet_wrap(~ bac)
regC.bac <- regC.bac + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regC.bac <- regC.bac + stat_smooth(method='lm',fullrange=F, se=T, size=2)
regC.bac <- regC.bac + labs(x= element_blank()) 
regC.bac <- regC.bac + labs(y= "Logged bacterial cell density (cells/µL)")
regC.bac <- regC.bac + theme(axis.title = element_text(face="bold", size=12))
regC.bac <- regC.bac + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))

bac.emtC <- emtrends(regC3, "bac", var = "logabs")
bac.emtC<-as.data.frame(bac.emtC)
bac.emtC

#Let's add these estimates to our SumC
Sum_LRRC$reg.mean<-bac.emtC$logabs.trend
Sum_LRRC$reg.SE<-bac.emtC$SE

#Let's also add this information to logC
bac.trend<-bac.emtC$logabs[2:12]
SE.trend<-bac.emtC$SE[2:12]

lrrC$reg.mean<-bac.trend
lrrC$reg.SE<-SE.trend

logemtC <- ggplot(lrrC,aes(y=reg.mean,x=LRR,colour=bac))+ geom_point()
logemtC <- logemtC + geom_errorbar(aes(ymin=reg.mean-reg.SE,ymax=reg.mean+reg.SE))
logemtC <- logemtC + geom_errorbar(aes(xmin=LRR-SE, xmax=LRR+SE))
logemtC <- logemtC + theme_classic() + ggtitle("Churchill") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
logemtC <- logemtC + theme(legend.title=element_blank())
logemtC <- logemtC + theme(legend.position = "none")
logemtC <- logemtC + labs(x= element_blank()) 
logemtC <- logemtC + labs(y= "Fitness regression")
logemtC <- logemtC + theme(axis.title = element_text(face="bold", size=12))
logemtC <- logemtC + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))

```

SECTION 5: Wellspring: Modelling.

```{r Wellspring models}

#How does bacterial inoculation affect growth?
modW_Grt<-lm(Grt~bac,data=dfW)
anova(modW_Grt)
summary(modW_Grt)
#not significant, but all 10 bacteria and bac 2 are almost significantly different from the mean. 

#What if we look at initial and final pixel count variation?
modW_pix<-lm(pix1~bac+pix0,data=dfW)
Anova(modW_pix, type=3)
summary(modW_pix)
#No change — bacteria remains non-significant

# Let's add in edge effects.
modW_pixgrt<-lm(pix1~bac+pix0+edge,data=dfW)
Anova(modW_pixgrt, type=3)
summary(modW_pixgrt)
#So edge is significant, nothing else changes.

#Let's try that as a random effect
lmer.grtW<-lmer(pix1~pix0 + bac +(1|edge),data=dfW)
summary(lmer.grtW)
Anova(lmer.grtW, type=3)

exactRLRT(lmer.grtW)
#Yep! Edge matters.

#How does bacterial identity and the presence of plants affect cell density?
modW_abs<-lm(logabs~bac*plt+edge,data=dfW)
anova(modW_abs)
summary(modW_abs)
#so bacterial identity, plant presence, and the interaction between them all matter here. Edge too!

regW<-lm(Grt~logabs+bac+edge,data=dfW)
Anova(regW, type = 3)
summary(regW)
#significant correlation b/w logabs and growth, edge nearly significant. No bac!

regW2<-lm(pix1~logabs+pix0+bac+edge,data=dfW)
Anova(regW2, type = 3)
summary(regW2)
#So regardless of how we measure growth rate, logged absolute count is correlated with duckweed fitness. This adds edge as a significant effect. 

#What about an interaction term? This will set up emmeans analysis too. 
regW3<-lm(Grt~logabs*bac+edge,data=dfW)
Anova(regW3, type = 3)
summary(regW3)
#Wait what? Now bac comes out as highly significant, so long as you include an interaction with the regression. (which is also significant)

regW4<-lm(pix1~logabs*bac + pix0+edge,data=dfW)
Anova(regW4, type = 3)
summary(regW4)

# So what do we make of this? (1) We see a correlation b/w duckweed and bacterial fitness UNTIL we incorporate and interaction. (2) If (but only if) we account for the interaction, we then see the effect of bacterial identity. (3) The interaction is also highly significant. (4) This suggests that the bacteria have very different correlations with DW fitness?

```

SECTION 6: Wellspring: Plotting.

```{r Wellspring plots}

dwW <- ggplot(Sum_LRRW,aes(y=mean,x=bac,colour=bac))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5)+geom_point(size=4.5)
dwW <- dwW + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
dwW <- dwW + scale_colour_manual(values=c("red3","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
dwW <- dwW + theme(legend.title=element_blank())
dwW <- dwW + theme(legend.position = "none")
dwW <- dwW + labs(x= element_blank()) 
dwW <- dwW + labs(y= element_blank())
dwW <- dwW + geom_hline(yintercept=23262.70, linetype="dashed", color = "red3",size=1)
dwW <- dwW + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))

#OK, we want to add a line based on additive interactive effects among bacteria
#Calculate the effect of each microbe on plant growth
base_grtW<-Sum_LRRW[1,3]
Sum_LRRW$bac_eff<-(Sum_LRRW$mean - base_grtW)/10
add_predW<-sum(Sum_LRRW$bac_eff[2:12]) +base_grtW

dwW <- dwW + geom_hline(yintercept=add_predW, linetype="dashed", color = "blue3",size=1)

#Alright, let's plot LogRRs.

logW_plt <- ggplot(lrrW,aes(y=LRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=LRR-SE,ymax=LRR+SE),width=0.5)+geom_point(size=4.5)
logW_plt <- logW_plt + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
logW_plt <- logW_plt + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
logW_plt <- logW_plt + theme(legend.title=element_blank())
logW_plt <- logW_plt + theme(legend.position = "none")
logW_plt <- logW_plt + labs(x= element_blank()) 
logW_plt <- logW_plt + labs(y= element_blank())
logW_plt <- logW_plt + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))
logW_plt <- logW_plt + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

# OK, bacteria.

melt_W_abs<-melt(dfW, id.vars=c("bac","plt"), measure.vars= "logabs", na.rm = T)
Sum_W_abs<- ddply(melt_W_abs, c("bac","plt","variable"), summarise,
                mean = mean(value), sd = sd(value), count=n(),
                sem = sd(value)/sqrt(length(value)))

for (i in 1:11){
  a<-i*2
  lrrW[i,5]<-log(Sum_W_abs[a+1,4]/Sum_W_abs[a,4])
  lrrW[i,6]<-Sum_W_abs[a+1,5]^2/(Sum_W_abs[a+1,6]*Sum_W_abs[a+1,4]^2) + Sum_W_abs[a,5]^2/(Sum_W_abs[1,6]*Sum_W_abs[1,4]^2)
}

names(lrrW)<-c('bac','LRR','var','SE','absLRR','absvar')
lrrW$absSE<-sqrt(lrrW$absvar)

absW <- ggplot(Sum_W_abs,aes(y=mean,x=bac,colour=bac,shape=plt))+geom_errorbar(aes(ymin=mean-sem,ymax=mean+sem),width=0.5, position=position_dodge(width=0.4)) +geom_point(position=position_dodge(width=0.4), size=4.5)
absW <- absW + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
absW <- absW + scale_colour_manual(values=c("red3","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
absW <- absW + theme(legend.title=element_blank())
absW <- absW + guides(colour='none')
absW <- absW + scale_shape_discrete(name = "Treatment", labels = c("Bacteria only", "Plants & Bacteria"))
absW <- absW + theme(legend.position = 'none')
absW <- absW + labs(x= element_blank()) 
absW <- absW + labs(y= element_blank())
absW <- absW + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))

#Let's collapse this to LogRR's? This plot would show the importance of plant presence to each bacteria

LRR_absW <- ggplot(lrrW,aes(y=absLRR,x=bac,colour=bac))+geom_errorbar(aes(ymin=absLRR-absSE,ymax=absLRR+absSE),width=0.5, position=position_dodge(width=0.4)) +geom_point(position=position_dodge(width=0.4), size=4.5)
LRR_absW <- LRR_absW + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
LRR_absW <- LRR_absW + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
LRR_absW <- LRR_absW + theme(legend.title=element_blank())
LRR_absW <- LRR_absW + guides(colour='none')
LRR_absW <- LRR_absW + theme(legend.title=element_blank())
LRR_absW <- LRR_absW + theme(legend.position = 'none')
LRR_absW <- LRR_absW + labs(x= element_blank()) 
LRR_absW <- LRR_absW + labs(y= element_blank())
LRR_absW <- LRR_absW + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))
LRR_absW <- LRR_absW + geom_hline(yintercept=0, linetype="dashed", color = "red3",size=1)

regW <- ggplot(dfW,aes(y=logabs,x=Grt))+ geom_point()
regW <- regW + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regW <- regW + stat_smooth(method='lm',fullrange=F, se=T, size=2)
regW <- regW + labs(x= element_blank()) 
regW <- regW + labs(y= element_blank()) 

dfW.plt<-subset(dfW, dfW$plt=='Y')

melt_W_abs.plt<-melt(dfW.plt, id.vars=c("bac"), measure.vars= "logabs", na.rm = T)
Sum_W_abs.plt<- ddply(melt_W_abs, c("bac","variable"), summarise,
                mean = mean(value), sd = sd(value), count=n(),
                sem = sd(value)/sqrt(length(value)))

Sum_LRRW$mean.abs<- Sum_W_abs.plt$mean
Sum_LRRW$se.abs<- Sum_W_abs.plt$sem
  
regW2 <- ggplot(Sum_LRRW,aes(x=mean,y=mean.abs,colour=bac))+geom_errorbar(aes(xmin=mean-sem,xmax=mean+sem)) +geom_point(size=4.5)
regW2 <- regW2 + geom_errorbar(aes(ymin=mean.abs-se.abs,ymax=mean.abs+se.abs))
regW2 <- regW2 + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regW2 <- regW2 + scale_colour_manual(values=c("red3","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
regW2 <- regW2 + theme(legend.title=element_blank())
regW2 <- regW2 + theme(legend.position = "none")
regW2 <- regW2 + labs(x= element_blank()) 
regW2 <- regW2 + labs(y= element_blank()) 

regWlRR <- ggplot(lrrW,aes(y=absLRR,x=LRR,colour=bac))+ geom_point()
regWlRR <- regWlRR + geom_errorbar(aes(ymin=absLRR-absSE,ymax=absLRR+absSE))
regWlRR <- regWlRR + geom_errorbar(aes(xmin=LRR-SE, xmax=LRR+SE))
regWlRR <- regWlRR + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regWlRR <- regWlRR + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))
regWlRR <- regWlRR + theme(legend.title=element_blank())
regWlRR <- regWlRR + theme(legend.position = "none")
regWlRR <- regWlRR + labs(x= element_blank()) 
regWlRR <- regWlRR + labs(y= element_blank()) 

regW.bac <- ggplot(dfW,aes(y=logabs,x=Grt))+ geom_point()
regW.bac <- regW.bac + facet_wrap(~ bac)
regW.bac <- regW.bac + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
regW.bac <- regW.bac + stat_smooth(method='lm',fullrange=F, se=T, size=2)
regW.bac <- regW.bac + labs(x= element_blank())  
regW.bac <- regW.bac + labs(y= element_blank())
regW.bac <- regW.bac + theme(axis.text.x = element_text(angle = 45, hjust=1,vjust=1))

bac.emtW <- emtrends(regW3, "bac", var = "logabs")
bac.emtW<-as.data.frame(bac.emtW)
bac.emtW

#Let's add these estimates to our SumW
Sum_LRRW$reg.mean<-bac.emtW$logabs.trend
Sum_LRRW$reg.SE<-bac.emtW$SE

#Let's also add this information to lrrW
bac.trend<-bac.emtW$logabs[2:12]
SE.trend<-bac.emtW$SE[2:12]

lrrW$reg.mean<-bac.trend
lrrW$reg.SE<-SE.trend

logemtW <- ggplot(lrrW,aes(y=reg.mean,x=LRR,colour=bac))+ geom_point()
logemtW <- logemtW + geom_errorbar(aes(ymin=reg.mean-reg.SE,ymax=reg.mean+reg.SE))
logemtW <- logemtW + geom_errorbar(aes(xmin=LRR-SE, xmax=LRR+SE))
logemtW <- logemtW + theme_classic() + ggtitle("Wellspring") + theme(plot.title = element_text(size=14, face='bold', hjust = 0.5))
logemtW <- logemtW + theme(legend.title=element_blank())
logemtW <- logemtW + theme(legend.position = "none")
logemtW <- logemtW + labs(x= element_blank()) 
logemtW <- logemtW + labs(y= element_blank()) 
logemtW <- logemtW + theme(axis.title = element_text(face="bold", size=12))
logemtW <- logemtW + scale_colour_manual(values=c("#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","#000000","blue3"))


```

SECTION 7: Putting figures together

```{r summary figs}

#1 — Raw duckweed growth ~ bac
plot_dw<-plot_grid(dwC, dwW, ncol=2,nrow=1, align='h')

x.grob_bac <- textGrob(expression(bold("Bacterial strain")), gp=gpar(fontsize=12))
grid.arrange(arrangeGrob(plot_dw, bottom = x.grob_bac))

#2 — LogRR's of dw grt
# Re-scale y axes
logC_plt <- logC_plt + ylim(-0.3,0.55)
logW_plt <- logW_plt + ylim(-0.3,0.55)

plot_dwLRR<-plot_grid(logC_plt, logW_plt, ncol=2,nrow=1, align='h')
grid.arrange(arrangeGrob(plot_dwLRR, bottom = x.grob_bac))

#3 - Bacterial 'fitness' ~ bac
#Relocate legend. 
absC <- absC + theme(legend.position = c(0.2,0.9))
plot_bac<-plot_grid(absC, absW, ncol=2,nrow=1, align='h')
grid.arrange(arrangeGrob(plot_bac, bottom = x.grob_bac))

#4 - LogRR of effect of plants on bacterial 'fitness' ~ bac
#Rescale ys
LRR_absC <- LRR_absC + ylim(-0.05,0.65)
LRR_absW <- LRR_absW + ylim(-0.05,0.65)

plot_bacLRR<-plot_grid(LRR_absC, LRR_absW, ncol=2,nrow=1, align='h')
grid.arrange(arrangeGrob(plot_bacLRR, bottom = x.grob_bac))

#5 - Regression of bacterial and dw fitness
plot_reg<-plot_grid(regC, regW, ncol=2,nrow=1, align='h')

x.grob_dwgrt <- textGrob(expression(bold("Duckweed growth (change in pixel count)")), gp=gpar(fontsize=12))
grid.arrange(arrangeGrob(plot_reg, bottom = x.grob_dwgrt))

#6 - Regression of bacterial and dw fitness (summary stats by bacteria)
plot_reg_sum<-plot_grid(regC2, regW2, ncol=2,nrow=1, align='h')
grid.arrange(arrangeGrob(plot_reg_sum, bottom = x.grob_dwgrt))

#7 - Regression of lRRs (effects of plts on bac & effects of bac on plants)
plot_regClRR<-plot_grid(regClRR, regWlRR, ncol=2,nrow=1, align='h')

x.grob_dwLRRgrt <- textGrob(expression(bold("Effect of bacterial inoculation (Log Response Ratio)")), gp=gpar(fontsize=12))
grid.arrange(arrangeGrob(plot_regClRR, bottom = x.grob_dwLRRgrt))

#8 - Bacteria-specific regressions
plot_reg.bac<-plot_grid(regC.bac, regW.bac, ncol=2,nrow=1, align='h')
grid.arrange(arrangeGrob(plot_reg.bac, bottom = x.grob_dwgrt))

#9 - Fitness regressions ~ effects on plant growth
plot_emt<-plot_grid(logemtC, logemtW, ncol=2,nrow=1, align='h')
grid.arrange(arrangeGrob(plot_emt, bottom = x.grob_dwLRRgrt))
```

